The emotion--facial expression link: Evidence from human and automatic expression recognition

### 2020-08-27 manuscript/manuscript_apa.Rmd
before revision

---
title             : "The emotion–facial expression link: Evidence from human and automatic expression recognition"
shorttitle        : "The emotion–facial expression link"

@@

keywords          : "emotion, facial expression, self-report, human observer, automatic recognition."
wordcount         : "7941"

bibliography      : ["manuscript_ref.bib"]

floatsintext      : no
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"

output: papaja::apa6_word

# output            :
#   bookdown::pdf_book:
#     toc: false
#     number_sections: false
#     base_format: papaja::apa6_pdf

@@

```{r setup, include = FALSE}
library(papaja)
library(kableExtra) # Tables
library(tidyverse) # Data wrangling & grammar of graphics
library(here) # Locate files relative to project root
library(caret) # Confusion matrices
```

```{r analysis-preferences}
set.seed(123) # Seed for random number generation
options(scipen = 999)# Disable scientific number format
knitr::opts_chunk$set(
  cache.extra = knitr::rand_seed, 
  message = FALSE, 
  warning = FALSE, 
  error = FALSE, 
  echo = FALSE
  )
```

@@

With the development of commercial automatic facial expression recognition tools [@dupre2018accuracy], industries and governments are gradually implementing this technology in order to monitor humans’ emotions in various scenarios (*e.g.*, in marketing, healthcare, and the automotive industry to name a few). This technology rests on the premise that facial expressions provide direct access to individuals’ subjective feelings, and that one can read the emotions displayed on a person’s face as one would an open book. This premise is derived from the "Basic Emotion View", a theory which suggests a one-to-one mapping between subective feeling and facial expression [@ekman1987universals; @ekman1988universality; @ekman1992argument; @ekman2007directed]. Even if this premise is central to the modern mainstream approach of human emotion, recent research in affective science is challenging it. Once the Basic Emotion View is briefly described, its foremost criticisms will be exposed. Inconsistencies and unpredicted findings come both from field observations and laboratory experiments. They relate to two different issues. The first issue is the sender’s production of spontaneous facial displays. The second issue relates to the receiver’s interpretation of these facial displays. Building on this evidence, and as an attempt to shed further light on the emotion–face link, the present study's main goal is to tackle these two issues at the same time. It aims at identifying the extent to which ordinary people’s experienced emotions are displayed through identifiable Emotional Facial Expressions (EFE) recognized as such both by human individuals, and by automatic facial expression recognition tools.

@@

```{r self-report-method}
self_report_gender <- self_report_data %>% 
  dplyr::group_by(genre_c) %>% 
  dplyr::summarise(n = n())

self_report_age <- self_report_data %>%
  dplyr::summarise(Age_m = mean(age), Age_sd = sd(age)) %>% 
  dplyr::mutate_all(round, 1)
```

For the emotion elicitation experiment, `r nrow(self_report_data)` encoding participants (`r self_report_gender[self_report_gender$genre_c == "F","n"]` females, `r self_report_gender[self_report_gender$genre_c == "H","n"]` males, *M*~age~ = `r self_report_age[,"Age_m"]`, *SD*~age~ = `r self_report_age[,"Age_sd"]`) were recruited to perform one out of 11 emotion elicitation tasks designed to trigger a positive, a specific negative or a neutral emotional state. Encoders’ faces were recorded using a hidden camera resulting `r nrow(self_report_data)` front facing 768x576 videos varying from `r min(metadata_video$ffprobe_duration)`s to `r max(metadata_video$ffprobe_duration)`s. These recordings form the DynEmo database [@tcherkassof2013dynemo].

@@

```{r human-recognition-method}
unique_ppt_count <- human_recognition_data %>% 
  dplyr::group_by(source,SEXE_Juge, C_Juge) %>% 
  dplyr::summarise(n = n())

unique_video_count <- human_recognition_data %>% 
  dplyr::select(source,SEXE_Juge, C_Juge, C_Video) %>% 
  unique() %>% 
  dplyr::group_by(C_Video) %>% 
  dplyr::summarise(n = n())
```

For the human facial expression recognition method, `r nrow(unique_ppt_count)` student participants were recruited to annotate `r nrow(unique_video_count)` out of the `r nrow(self_report_data)` videos, therefore only the `r nrow(unique_video_count)` annotated videos were analyzed in this study. Because videos have different durations, participants had to annotate a series of video corresponding to 30min long in total. Each video was annotated `r mean(unique_video_count$n) %>% round(0)` times on average (*SD* = `r sd(unique_video_count$n) %>% round(0)`).

@@

where *i* is one of the `r nrow(unique_video_count)` videos, *j* is one of the six “basic” emotion labels, *k* for each second of the video.

@@

The `r nrow(unique_video_count)` annotated video were processed with Affdex (SDK v3.4.1). Affdex is an automatic facial expression recognition classifier developed and distributed by Affectiva, which is a spin-off company resulting from the research activities of MIT media lab created in 2009 [@mcduff2016affdex]. Affdex’s algorithm uses Histogram of Oriented Gradient (HOG) features and Support Vector Machine (SVM) classifiers in order to recognize facial expressions. For each video frame, Affdex identifies the probability $p_{video_{i}.label_{j}.t_{k}}$ from 0 to 100 (rescaled to 0 to 1 for the analysis) of the face as expressing one of the six basic emotion labels (*i.e.*, *anger*, *disgust*, *fear*, *happiness*, *surprise* and *sadness*) as well as additional psychological states such as *valence*, *engagement* or *contempt*, and facial features such as *cheek raise*, *eye widen* or *jaw drop*.

@@

where *i* is one of the `r nrow(unique_video_count)` videos, *j* is one of the six “basic” emotion labels, *k* for each second of the *n* second video or for each frame of the *f* frame video.

@@

corr_hr_ar <- cor.test(
  recognition_result$hr_score, 
  recognition_result$ar_score, 
  method = "pearson",
  alternative = "two.sided"
  ) %>% 
  papaja::apa_print()

# sr_n <- recognition_result %>% 
#   dplyr::filter(sr_score == 1) %>% 
#   dplyr::group_by(list_emotion) %>% 
#   dplyr::tally()
```

@@

```{r sr-hr}
comparison_sr_hr <- dplyr::inner_join(self_report_score,human_recognition_score, by = "C_Video") %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(hr_emotion != "undetermined") %>% 
  dplyr::filter(sr_emotion != "undetermined") %>% 
  dplyr::mutate_if(is.character, as.factor)

@@

confusionMatrix_sr_hr_freq %>% 
  ggplot(mapping = aes(x = sr_emotion, y = hr_emotion)) +
  geom_tile(aes(fill = prop_sr), colour = "white") +
  geom_text(
    aes(label = paste0(scales::percent(prop_sr), "\n(", Freq,"/",n_sr, ")")),
    color = "black",
    size = 4,
    family="serif",
    parse = FALSE,
    lineheight = 0.7)+
  scale_fill_gradient(
    name = "Proportion of Recognized\nSelf-Reported Emotion",
    low = "white", 
    high = "red", 
    labels = scales::percent,
    limits = c(0,1)
  ) +
  scale_x_discrete(name = "Self-Reports") +
  scale_y_discrete(name = "Human Observers") +
  theme_minimal() +
  theme(text = element_text(size=16,family="serif"),
        axis.text.x = element_text(size=16, angle = 45, hjust = 0.75,vjust=0.9),
        axis.text.y = element_text(size=16, hjust = 0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        legend.text = element_text(size=8),
        legend.position = "bottom")
```

@@

```{r confusionTable-sr-hr, results="asis"}
confusionMatrix_sr_hr_table <- confusionMatrix_sr_hr %>%
  magrittr::use_series(byClass) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("Emotion") %>%
  dplyr::mutate(Emotion = gsub(pattern = "Class: ",replacement = "",x = Emotion)) %>% 
  dplyr::select(Emotion, Sensitivity, Specificity, Precision, F1) %>% 
  dplyr::mutate_if(is.numeric,round,2) %>% 
  # replace(is.na(.), "\\textit{na.}")
  replace(is.na(.), "na.")

confusionMatrix_sr_hr_table %>%
  # knitr::kable(
  #   "latex",
  #   caption = "(ref:confusionTable-sr-hr)",
  #   booktabs = TRUE,
  #   digits = 2,
  #   linesep = "",
  #   escape = FALSE,
  #   align = c('l', rep('c', 4)),
  #   longtable = T
  # ) %>%
  # kableExtra::kable_styling(
  #   latex_options = "HOLD_position",
  #   font_size = 8,
  #   full_width = TRUE 
  # ) %>%
  # kableExtra::footnote(
  #   general_title = "",
  #   general = "Note. na. values are produced when not enough data are available to compute accuracy indicators.", 
  #   escape = FALSE,
  #   footnote_as_chunk = TRUE,
  #   threeparttable = TRUE
  # )
  papaja::apa_table(
    caption = "(ref:confusionTable-sr-hr)",
    note = "na. values are produced when not enough data are available to compute accuracy indicators.",
    escape = TRUE
  )
```

@@

```{r sr-ar}
comparison_sr_ar <- dplyr::inner_join(self_report_score,automatic_recognition_score, by = "C_Video") %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(ar_emotion != "undetermined") %>% 
  dplyr::filter(sr_emotion != "undetermined") %>% 
  dplyr::mutate_if(is.character,as.factor)

@@

confusionMatrix_sr_ar_freq %>% 
  ggplot(mapping = aes(x = sr_emotion, y = ar_emotion)) +
  geom_tile(aes(fill = prop_sr), colour = "white") +
  geom_text(
    aes(label = paste0(scales::percent(prop_sr), "\n(", Freq,"/",n_sr, ")")),
    color = "black",
    size = 4,
    family="serif",
    parse = FALSE,
    lineheight = 0.7)+
  scale_fill_gradient(
    name = "Proportion of Recognized\nSelf-Reported Emotion",
    low = "white", 
    high = "red", 
    labels = scales::percent,
    limits = c(0,1)
  ) +
  scale_x_discrete(name = "Self-Reports") +
  scale_y_discrete(name = "Automatic Classifier") +
  theme_minimal() +
  theme(text = element_text(size=16,family="serif"),
        axis.text.x = element_text(size=16, angle = 45, hjust = 0.75,vjust=0.9),
        axis.text.y = element_text(size=16, hjust = 0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        legend.text = element_text(size=8),
        legend.position = "bottom")
```

@@

```{r confusionTable-sr-ar, results="asis"}
confusionMatrix_sr_ar_table <- confusionMatrix_sr_ar %>%
  magrittr::use_series(byClass) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("Emotion") %>%
  dplyr::mutate(Emotion = gsub(pattern = "Class: ", replacement = "", x = Emotion)) %>% 
  dplyr::select(Emotion, Sensitivity, Specificity, Precision, F1) %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>% 
  #replace(is.na(.), "\\textit{na.}")
  replace(is.na(.), "na.")

confusionMatrix_sr_ar_table %>%
  # knitr::kable(
  #   "latex",
  #   caption = "(ref:confusionTable-sr-ar)",
  #   booktabs = T,
  #   digits = 2,
  #   linesep = "",
  #   escape = FALSE,
  #   align = c('l',rep('c', 4)),
  #   longtable = T
  # ) %>%
  # kableExtra::kable_styling(
  #   latex_options = c("HOLD_position"),
  #   font_size = 8,
  #   full_width = TRUE
  #   ) %>%
  # kableExtra::footnote(
  #   general_title = "",
  #   general = "Note. na. values are produced when not enough data are available to compute accuracy indicators.", 
  #   escape = FALSE,
  #   footnote_as_chunk = TRUE,
  #   threeparttable = TRUE
  #   ) 
  papaja::apa_table(
    caption = "(ref:confusionTable-sr-ar)",
    note = "na. values are produced when not enough data are available to compute accuracy indicators.",
    escape = TRUE
  )
```

@@

```{r confusionMatrix-hr-ar, fig.height=6, out.width ="\\textwidth", fig.pos = "!h", fig.cap="(ref:confusionMatrix-hr-ar)"}
comparison_hr_ar <- dplyr::inner_join(human_recognition_score,automatic_recognition_score, by = "C_Video") %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(ar_emotion != "undetermined") %>% 
  dplyr::filter(hr_emotion != "undetermined") %>% 
  dplyr::mutate_if(is.character, as.factor)

@@

confusionMatrix_hr_ar_freq %>% 
  ggplot(mapping = aes(x = hr_emotion, y = ar_emotion)) +
  geom_tile(aes(fill = prop_hr), colour = "white") +
  geom_text(
    aes(label = paste0(scales::percent(prop_hr), "\n(", Freq, "/", n_hr, ")")),
    color = "black",
    size = 4,
    family="serif",
    parse = FALSE,
    lineheight = 0.7)+
  scale_fill_gradient(
    name = "Proportion Recognized Emotion",
    low = "white", 
    high = "red", 
    labels = scales::percent,
    limits = c(0,1)
  ) +
  scale_x_discrete(name = "Human Observers") +
  scale_y_discrete(name = "Automatic Classifier") +
  theme_minimal() +
  theme(text = element_text(size=16,family="serif"),
        axis.text.x = element_text(size=16, angle = 45, hjust = 0.75,vjust=0.9),
        axis.text.y = element_text(size=16, hjust = 0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        legend.text = element_text(size=8),
        legend.position = "bottom")
```

@@

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

>>>>

---
title             : "The emotion–facial expression link: Evidence from human and automatic expression recognition"
shorttitle        : "The emotion facial expression link"

@@

keywords          : "emotion, facial expression, self-report, human observer, automatic recognition."
wordcount         : "7943"

bibliography      : ["bib/manuscript_ref.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa7"
classoption       : "doc"

#output: papaja::apa6_word

output            :
  bookdown::pdf_book:
    toc: false
    number_sections: false
    base_format: papaja::apa6_pdf

@@

```{r setup, include = FALSE}
library(tidyverse) # Data wrangling & grammar of graphics
library(here) # Locate files relative to project root
library(papaja) # Manuscript design and results
library(kableExtra) # Tables
library(caret) # Confusion matrices
```

```{r analysis-preferences}
set.seed(123) # Seed for random number generation
options(scipen = 999)# Disable scientific number format
knitr::opts_chunk$set(
  cache.extra = knitr::rand_seed,
  cache = TRUE,
  message = FALSE, 
  warning = FALSE, 
  error = FALSE, 
  echo = FALSE
  )
```

@@

With the development of commercial automatic facial expression recognition tools [@dupre2018accuracy], industries and governments are gradually implementing this technology in order to monitor humans’ emotions in various scenarios (*e.g.*, in marketing, healthcare, and the automotive industry to name a few). This technology rests on the premise that facial expressions provide direct access to individuals’ subjective feelings, and that one can read the emotions displayed on a person’s face as one would an open book. This premise is derived from the "Basic Emotion View", a theory which suggests a one-to-one mapping between subjective feeling and facial expression [@ekman1987universals; @ekman1988universality; @ekman1992argument; @ekman2007directed]. Even if this premise is central to the modern mainstream approach of human emotion, recent research in affective science is challenging it. Once the Basic Emotion View is briefly described, its foremost criticisms will be exposed. Inconsistencies and unpredicted findings come both from field observations and laboratory experiments. They relate to two different issues. The first issue is the sender’s production of spontaneous facial displays. The second issue relates to the receiver’s interpretation of these facial displays. Building on this evidence, and as an attempt to shed further light on the emotion–face link, the present study's main goal is to tackle these two issues at the same time. It aims at identifying the extent to which ordinary people’s experienced emotions are displayed through identifiable Emotional Facial Expressions (EFE) recognized as such both by human individuals, and by automatic facial expression recognition tools.

@@

```{r self-report-method}
self_report_gender <- self_report_data %>% 
  dplyr::count(genre_c) %>% 
  dplyr::pull(n, genre_c)

self_report_age <- self_report_data %>%
  dplyr::summarise(
    age_m = mean(age) %>% round(1), 
    age_sd = sd(age) %>% round(1)
  )
```

For the emotion elicitation experiment, `r nrow(self_report_data)` encoding participants (`r self_report_gender["F"]` females, `r self_report_gender["H"]` males, *M*~age~ = `r self_report_age["age_m"]`, *SD*~age~ = `r self_report_age["age_sd"]`) were recruited to perform one out of 11 emotion elicitation tasks designed to trigger a positive, a specific negative or a neutral emotional state. Encoders’ faces were recorded using a hidden camera resulting `r nrow(self_report_data)` front facing 768x576 videos varying from `r min(metadata_video$ffprobe_duration)`s to `r max(metadata_video$ffprobe_duration)`s. These recordings form the DynEmo database [@tcherkassof2013dynemo].

@@

```{r human-recognition-method}
unique_ppt_count <- human_recognition_data %>% 
  dplyr::count(source, SEXE_Juge, C_Juge)

unique_video_count <- human_recognition_data %>% 
  dplyr::distinct(source, SEXE_Juge, C_Juge, C_Video) %>% 
  dplyr::count(C_Video) %>% 
  dplyr::summarise(
    vid_n = n(),
    vid_m = mean(n) %>% round(0), 
    vid_sd = sd(n) %>% round(0)
  )
```

For the human facial expression recognition method, `r nrow(unique_ppt_count)` student participants were recruited to annotate `r unique_video_count["vid_n"]` out of the `r nrow(self_report_data)` videos, therefore only the `r unique_video_count["vid_n"]` annotated videos were analyzed in this study. Because videos have different duration, participants had to annotate a series of video corresponding to 30min long in total. Each video was annotated `r unique_video_count["vid_m"]` times on average (*SD* = `r unique_video_count["vid_sd"]`).

@@

where *i* is one of the `r unique_video_count["vid_n"]` videos, *j* is one of the six “basic” emotion labels, *k* for each second of the video.

@@

The `r unique_video_count["vid_n"]` annotated video were processed with Affdex (SDK v3.4.1). Affdex is an automatic facial expression recognition classifier developed and distributed by Affectiva, which is a spin-off company resulting from the research activities of MIT media lab created in 2009 [@mcduff2016affdex]. Affdex’s algorithm uses Histogram of Oriented Gradient (HOG) features and Support Vector Machine (SVM) classifiers in order to recognize facial expressions. For each video frame, Affdex identifies the probability $p_{video_{i}.label_{j}.t_{k}}$ from 0 to 100 (rescaled to 0 to 1 for the analysis) of the face as expressing one of the six basic emotion labels (*i.e.*, *anger*, *disgust*, *fear*, *happiness*, *surprise* and *sadness*) as well as additional psychological states such as *valence*, *engagement* or *contempt*, and facial features such as *cheek raise*, *eye widen* or *jaw drop*.

@@

where *i* is one of the `r unique_video_count["vid_n"]` videos, *j* is one of the six “basic” emotion labels, *k* for each second of the *n* second video or for each frame of the *f* frame video.

@@

corr_hr_ar <- 
  cor.test(
    recognition_result$hr_score, 
    recognition_result$ar_score, 
    method = "pearson",
    alternative = "two.sided"
  ) %>% 
  papaja::apa_print()
```

@@

```{r sr-hr}
comparison_sr_hr <- self_report_score %>% 
  dplyr::inner_join(human_recognition_score, by = "C_Video") %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(hr_emotion != "undetermined") %>% 
  dplyr::filter(sr_emotion != "undetermined") %>% 
  dplyr::mutate_if(is.character, as.factor)

@@

confusionMatrix_sr_hr_freq %>%
  ggplot(mapping = aes(x = sr_emotion, y = hr_emotion)) +
  geom_tile(aes(fill = prop_sr), colour = "white") +
  geom_text(
    aes(label = paste0(
      scales::percent(prop_sr, accuracy = 1), "\n(", Freq, "/", n_sr, ")"
    )),
    color = "black",
    size = 4,
    family = "serif",
    parse = FALSE,
    lineheight = 0.7
  ) +
  scale_fill_gradient(
    name = "Proportion of Recognized\nSelf-Reported Emotion",
    low = "white",
    high = "red",
    labels = scales::percent,
    limits = c(0, 1)
  ) +
  scale_x_discrete(name = "Self-Reports") +
  scale_y_discrete(name = "Human Observers") +
  theme_minimal() +
  theme(
    text = element_text(size = 16, family = "serif"),
    axis.text.x = element_text(size = 16, angle = 45, hjust = 0.75, vjust = 0.9),
    axis.text.y = element_text(size = 16, hjust = 0.5),
    axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
    legend.text = element_text(size = 8),
    legend.position = "bottom"
  )
```

@@

```{r confusionTable-sr-hr, results="asis"}
confusionMatrix_sr_hr_table <- confusionMatrix_sr_hr %>%
  magrittr::use_series(byClass) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("Emotion") %>%
  dplyr::mutate(Emotion = gsub(pattern = "Class: ", replacement = "", x = Emotion)) %>% 
  dplyr::select(Emotion, Sensitivity, Specificity, Precision, F1) %>% 
  dplyr::mutate_if(is.numeric, round,2) %>% 
  replace(is.na(.), "na.")

confusionMatrix_sr_hr_table %>%
  papaja::apa_table(
    caption = "(ref:confusionTable-sr-hr)",
    note = "na. values are produced when not enough data are available to compute accuracy indicators.",
    escape = TRUE
  )
```

@@

```{r sr-ar}
comparison_sr_ar <- self_report_score %>% 
  dplyr::inner_join(automatic_recognition_score, by = "C_Video") %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(ar_emotion != "undetermined") %>% 
  dplyr::filter(sr_emotion != "undetermined") %>% 
  dplyr::mutate_if(is.character, as.factor)

@@

confusionMatrix_sr_ar_freq %>%
  ggplot(mapping = aes(x = sr_emotion, y = ar_emotion)) +
  geom_tile(aes(fill = prop_sr), colour = "white") +
  geom_text(
    aes(label = paste0(
      scales::percent(prop_sr, accuracy = 1), "\n(", Freq, "/", n_sr, ")"
    )),
    color = "black",
    size = 4,
    family = "serif",
    parse = FALSE,
    lineheight = 0.7
  ) +
  scale_fill_gradient(
    name = "Proportion of Recognized\nSelf-Reported Emotion",
    low = "white",
    high = "red",
    labels = scales::percent,
    limits = c(0, 1)
  ) +
  scale_x_discrete(name = "Self-Reports") +
  scale_y_discrete(name = "Automatic Classifier") +
  theme_minimal() +
  theme(
    text = element_text(size = 16, family = "serif"),
    axis.text.x = element_text(size = 16, angle = 45, hjust = 0.75, vjust = 0.9 ),
    axis.text.y = element_text(size = 16, hjust = 0.5),
    axis.title.y = element_text(margin = margin( t = 0, r = 20, b = 0, l = 0)),
    legend.text = element_text(size = 8),
    legend.position = "bottom"
  )
```

@@

```{r confusionTable-sr-ar, results="asis"}
confusionMatrix_sr_ar_table <- confusionMatrix_sr_ar %>%
  magrittr::use_series(byClass) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("Emotion") %>%
  dplyr::mutate(Emotion = gsub(pattern = "Class: ", replacement = "", x = Emotion)) %>% 
  dplyr::select(Emotion, Sensitivity, Specificity, Precision, F1) %>% 
  dplyr::mutate_if(is.numeric, round, 2) %>% 
  replace(is.na(.), "na.")

confusionMatrix_sr_ar_table %>%
  papaja::apa_table(
    caption = "(ref:confusionTable-sr-ar)",
    note = "na. values are produced when not enough data are available to compute accuracy indicators.",
    escape = TRUE
  )
```

@@

```{r confusionMatrix-hr-ar, fig.height=6, out.width ="\\textwidth", fig.pos = "!h", fig.cap="(ref:confusionMatrix-hr-ar)"}
comparison_hr_ar <- human_recognition_score %>% 
  dplyr::inner_join(automatic_recognition_score, by = "C_Video") %>% 
  dplyr::ungroup() %>% 
  dplyr::filter(ar_emotion != "undetermined") %>% 
  dplyr::filter(hr_emotion != "undetermined") %>% 
  dplyr::mutate_if(is.character, as.factor)

@@

confusionMatrix_hr_ar_freq %>%
  ggplot(mapping = aes(x = hr_emotion, y = ar_emotion)) +
  geom_tile(aes(fill = prop_hr), colour = "white") +
  geom_text(
    aes(label = paste0(
      scales::percent(prop_hr, accuracy = 1), "\n(", Freq, "/", n_hr, ")"
    )),
    color = "black",
    size = 4,
    family = "serif",
    parse = FALSE,
    lineheight = 0.7
  ) +
  scale_fill_gradient(
    name = "Proportion Recognized Emotion",
    low = "white",
    high = "red",
    labels = scales::percent,
    limits = c(0, 1)
  ) +
  scale_x_discrete(name = "Human Observers") +
  scale_y_discrete(name = "Automatic Classifier") +
  theme_minimal() +
  theme(
    text = element_text(size = 16, family = "serif"),
    axis.text.x = element_text(size = 16, angle = 45, hjust = 0.75, vjust = 0.9),
    axis.text.y = element_text(size = 16, hjust = 0.5),
    axis.title.y = element_text(margin = margin(t = 0,r = 20, b = 0, l = 0)),
    legend.text = element_text(size = 8),
    legend.position = "bottom"
  )
```

@@

# References
```{r create_r-references}
#r_refs(file = "bib/r-references.bib")
```
